% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      

\textit{No man is an island, entire of itself; every man is a piece of the continent, a part of the main}\footnote{\textit{John Donne, Devotions upon Emergent Occasions}}. 
This is especially true in Experimental Particle Physics, which in recent decades has required large collaborations of people working together to explore the new frontiers. The making of this thesis is no different; I am deeply indebted to a great number of people who have helped me along the way. Here are some small words of thanks to you all.

To Armin Reichold, thank you so much for being my supervisor: always being there to ask the right questions about my work, and giving me advice about what to look at next. I made it through fighting SMELLIE thanks to your help. I've had so much fun doing research with you, learning so much thanks in part to your words to me: ``No black boxes''.

To Steve Biller and Jeff Tseng, your advice on matters of analysis, statistics, and computing have been invaluable. My work would be a shambles otherwise. Thank you also for building such a welcoming place to do Physics.

To Kim Proudfoot and Sue Geddes, who are the primary reason why the Particle Physics sub-department runs in any capacity. Also, to the IT Support staff; my work literally could not have been done without you guys keeping the interactive machines and internet connections working nicely. I'm sorry, Vip, for blocking the queue that time.

To the ever-growing family of colleagues and friends who I have had the pleasure of working in the SNO+ office with: Tereza, Iwan, Josh, Rafael, Cal, Gulliver, Abi, Jasmine, Qingyang, and Ellie. Special thanks to Josie for being an awesome thesis-writing buddy, and a brilliant friend. Also, to the elite strike squad of postdocs: Ed, Will, Ana Sofia, and Ben. I would be remiss in forgetting all the folks who have worked on SMELLIE, including Esther Turner and Jeff Lidgard. Jeff, thanks so much for being willing to fight through SMELLIE `integration hell' with me.

To Vic, Sierra, Caroline, Steph, Cindy, Matt, Mark, Aleksandra, Christine, and Ryan, thanks so much for making Sudbury so inviting whilst I was there; be it stuck underground without power, singing at Little Montreal, sliding on inflatables on Ramsey Lake, or getting stuck in Espanola. James and Rafael (again), it was great fun being housemates. Juliette, thanks for being my partner-in-crime as YM representatives: I hope your canoe is still okay.

To my friends outside the SNO+ cult, you are what makes life worth living: Eimear, Soniya, Ynyr, Ciaran, Niamh, Steph, Gwen, Sol, Ben, and so many others. Also, to everyone I've played with in Quadball (n\'{e}e Quidditch). Never Forget to be Awesome.

And finally, to my family: Mum, Dad, Joel, Ben, Leo, and Crumble. Thank you all for being so loving and fun, even after so many months in lockdown together. I would not be here without you. \textit{...All shall be well, and all shall be well, and all manner of thing shall be well.}\footnote{\textit{Julian of Norwich}}

\end{acknowledgements}
